AP/PA Tables ITHIM Global

### 2021-04-27 code/producing_trips_rd/trip-summary.Rmd
Updating summary files

```
```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
(readxl::read_excel("C:/Users/danie/Documents/Daniel_Gil/Consultorias/2020/WorldBank/ITHIM-R/code/producing_trips_rd/Travel_survey_details.xlsx")
  ) %>% kbl() %>% kable_classic()

@@

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value

@@

```{r, include = TRUE,  echo= FALSE, results='asis'}
kable(trip_summary) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T)

>>>>

```{r,  comment=NA, message=FALSE, warning=FALSE, prompt=FALSE, cache=FALSE, echo=F}
# (readxl::read_excel("C:/Users/danie/Documents/Daniel_Gil/Consultorias/2020/WorldBank/ITHIM-R/code/producing_trips_rd/Travel_survey_details.xlsx")
#   ) %>% kbl() %>% kable_classic()

@@

trip <- read_csv("../../data/local/cape_town/cape_town_trip.csv",
                 guess_max = 100000)
quality_check(trip)
trip_summary$Cape_Town <- value
```

## summary table
```{r, include = TRUE,  echo= FALSE, results='asis'}
kable(trip_summary) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 14, fixed_thead = T)

@@

### 2021-04-27 summary_tables.Rmd
Updating summary files

@@

>>>>

```
# **1st option**
## Scenario definition 
Table displays highest propensity for each distance category, for a given mode.

@@

# **2nd option**

kable(scen_prop, headings = "Scenario Proportions")
ggplot(as.data.frame(scen_prop) %>% rownames_to_column("scenario") %>% 
         pivot_longer(!scenario, names_to = "distance_cat", 
                      values_to = "values") %>% 
         mutate(scenario = factor(scenario, 
                                  levels = c("pedestrian_scen", "cycle_scen",
                                             "car_scen", "motorcycle_scen",
                                             "bus_scen"))
                ), 
       aes(scenario, values, fill = distance_cat)) + geom_col() + 
  facet_grid(~ distance_cat) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "none")
```

```{r load_tidyverse2, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```

```{r trip_mode_dist = "asis", echo = F, message = F}

for (city in cities) {
  cat("\n \n")
  cat( paste0('### **', city, '** \n' )) 
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% 
    summarise(uid = n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% 
    group_by(trip_mode, scenario) %>% 
    summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% 
    spread(key = trip_mode, value = p) %>% 
    mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

  if (length(trip_prop) == 0) {
    trip_prop <- td1 %>% dplyr::select(stage_mode)
  }

  y <- ggplot(td %>% rownames_to_column("stage_mode") %>% 
         pivot_longer(!stage_mode, names_to = "scenario", 
                      values_to = "proportion") %>% 
           mutate(scenario = factor(scenario,
                                    levels = c("baseline", "pedestrian_scen",
                                               "cycle_scen", "car_scen",
                                               "motorcycle_scen", "bus_scen")),
                  stage_mode = factor(stage_mode,
                                      levels = c("car", "motorcycle", "bus",
                                                 "pedestrian", "taxi", "rail",
                                                 "cycle")),
                  proportion = as.numeric(proportion)) %>% 
           dplyr::filter(stage_mode != "row_sums"), 
       aes(scenario, proportion, fill = stage_mode)) + geom_col() + 
  facet_grid(~ stage_mode) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "none")

  cat(" ")
  print(y)
  cat("\n ")
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

ggplot(trip_prop %>% 
         pivot_longer(!stage_mode, names_to = "city", 
                      values_to = "proportion") %>% 
         dplyr::filter(stage_mode != "Total") %>%
         mutate(stage_mode = factor(stage_mode, 
                                    levels = c("car", "motorcycle", "bus",
                                               "pedestrian", "taxi", "rail",
                                               "cycle"))), 
       aes(stage_mode, proportion, fill = city)) + geom_col() + 
  facet_grid(~ city) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "none")

```{r unload_tidyverse2, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

for (city in cities) {
  cat("\n \n")
  cat( paste0('### **', city, '** \n' )) 
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)

  y <- ggplot(td %>% 
         pivot_longer(!stage_mode, names_to = "scenario", 
                      values_to = "distance") %>% 
           mutate(scenario = factor(scenario,
                                    levels = c("Baseline", "pedestrian_scen",
                                               "cycle_scen", "car_scen",
                                               "motorcycle_scen", "bus_scen")),
                  stage_mode = factor(stage_mode,
                                      levels = c("car", "motorcycle", "bus",
                                                 "pedestrian", "taxi", "rail",
                                                 "cycle"))),
         aes(scenario, distance, fill = stage_mode)) + geom_col() + 
    facet_grid(~ stage_mode) +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "none")

  cat(" ")
  print(y)
  cat("\n ")
  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n") 
}

ggplot(trip_dist %>% 
         pivot_longer(!stage_mode, names_to = "city", 
                      values_to = "distance") %>% 
         mutate(stage_mode = factor(stage_mode, 
                                    levels = c("car", "motorcycle", "bus",
                                               "pedestrian", "taxi", "rail",
                                               "cycle", "Total"))), 
       aes(stage_mode, distance, fill = city)) + geom_col() + 
  facet_grid(~ city) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "none")

kable(trip_dist, caption = "Avg. distance per person (km) per day across all case studies")
```

### 2021-04-27 summary_tables_PA_AP.Rmd
Updating summary files

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)
library(plotly)
library(htmltools)

@@

>>>>

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)
#library(plotly)
#library(htmltools)

@@

# **2nd option**

# PM 2.5 summary and CO2
```{r message=FALSE, warning=FALSE, echo=FALSE}
# I have to keep the first chunk of code to run this part
# high<- c(70, 25, 150,60)
# low<- c(40,15,100,40)
# l <- htmltools::tagList()
for (x in 1:length(cities)) {
  # print(cities[x])
  cat("\n \n")
  cat( paste0('## **', cities[x], '** \n' )) 
  # Emission inventory
  modes <- names(unlist(io[[cities[x]]]$PM_emission_inventory))
  emissions <- as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  city_emissions <- cbind(as.data.frame(modes),                           as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2] <- "emissions"
  select <- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes <- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)] <- "other"
  summary <- city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2] <- cities[x]
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits = 1)
  summary <- as.data.frame(summary)
  summary[nrow(summary)+1,1] <- "Transport share"
  summary[nrow(summary),2] <- as.character(round(pm_trans_share[[cities[x]]] * 100))
  summary[nrow(summary)+1,1] <- "PM2.5 Conc"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  io[[cities[x]]]$summary_emission <- summary

  # PM 2.5 table and plot
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11] <- c("Baseline","Walking",
                                                        "Bicycling", "Driving",
                                                        "Motorcycling", 
                                                        "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:`Public Transport`, factor_key = TRUE)

  summary2 <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)))
  summary2 <- cbind(summary2$scenario, round(summary2[,2:5], digits = 1))
  summary2$change_PM <- round(io[[cities[x]]]$outcomes$scenario_pm - io[[cities[x]]]$outcomes$scenario_pm[1], digits = 2)
  names(summary2)[1] <- "Scenario"

  # Plot
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) +
    labs(y = "Daily PM2.5 Concentration", x = "Scenarios")

  # CO2
  td <- round(colSums(io[[cities[x]]]$outcomes$co2_conc, na.rm = T), 1) %>%
    as.data.frame() %>% tibble::rownames_to_column()
  #names(td) <- c('Scenario', cities[x])
  names(td) <- c('Scenario', 'CO2')
  td$Scenario <- c("Baseline","Walking", "Bicycling", "Driving", "Motorcycling",
                   "Public Transport")

  cat("\n \n")
  cat( paste('#### Boxplot of Individual-level PM2.5 concentrations \n' ))
  print(y)

  cat("\n \n")
  cat( paste('#### Emission inventory \n' )) 
  print(kable(summary))

  cat("\n \n")
  cat( paste('#### Descriptive table of Individual-level PM2.5 concentrations and CO2 emissions\n' ))
  print(kable(cbind(summary2, td), caption = cities[x]))

```{r, message=FALSE, warning=FALSE, echo=FALSE}
limit = 100
for (x in 1:length(cities)) {
  names(io[[cities[x]]]$outcomes$mmets)[5:10] <- c("Baseline","Walking",
                                                   "Bicycling", "Driving",
                                                   "Motorcycling", 
                                                   "Public Transport")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, Baseline:`Public Transport`, factor_key = TRUE)
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) + geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    labs(y = "Weekly MMET", x = "Scenarios") + ylim(0, limit)
  print(y)
